\label{MEsection}
The event-mixing technique is used for correcting the raw correlation distribution for effects arising
from the detector limited acceptance in rapidity and detector spatial inhomogeneities. The calculation of the Event
Mixing correlation distribution is performed online.%, following the strategy and the code developed for the \textit{PWGCF} correlation analyses.
An event pool is created, where events preceding the one containing a D candidate are stored based on their properties (position of the vertex along the z axis and multiplicity).
Each time a D meson candidate is found in an event, only the events contained in the same pool as the event under analysis is used to evaluate the correlations for the event mixing correction.% the correlation analysis on the mixed events is performed if the pool satisfies the conditions defined at its creation, being the same as described for the pp analysis (As well as the conditions for refreshing the pools).

The multiplicity and z vertex position bins for the pools used in the p-Pb analysis are the following:
\begin{itemize}
\item Multiplicity bins: $\left(0,40\right);\left(40,65\right);\left(65,+\infty\right)$
\item Vertex z $(cm)$ = $\left(-10,-2.5\right);\left(-2.5,2.5\right);\left(2.5,10\right)$
\end{itemize}
%(\ref{tab:em})


In an ideal case, the mixed event distribution is expected to have a constant flat distribution as function of $\Delta\phi$ and a triangular shaped distribution in $\Delta\eta$
deriving from the limited $\eta$ acceptance of the detector. The obtained distribution is used as a weight in each correlation bin, i.e, the corrected correlation distribution is calculated as follows:
\begin{equation}
\label{eq:mixing}
\frac{dN^{corr}\left(\Delta\phi \Delta\eta\right)}{d\Delta\phi d\Delta\eta} = \frac{\frac{dN^{SE}\left(\Delta\phi \Delta\eta\right)}{d\Delta\phi d\Delta\eta} }{\frac{dN^{ME}\left(\Delta\phi \Delta\eta\right)}{d\Delta\phi d\Delta\eta} }\frac{dN^{ME}\left(0,  0\right)}{d\Delta\phi d\Delta\eta}
\end{equation}
In the previous equation, the last term stands for the average of the bins in the region $-0.2 < \Delta\eta < 0.2$, $-0.2 < \Delta\phi < 0.2$ (multiple bins are used to minimize the effect of statistical fluctuations on the normalization of the mixed-event plots).

The mixed-event correlation distributions are built in both D meson signal and sideband regions. Both are
corrected with the relative distributions. An example of the mixed event distribution is shown in Fig.~\ref{fig:DplusSEbyMEPlots1} (middle panels). The expected triangular
shape in $\Delta\eta$ addresses the effect of the limited detector pseudo-rapidity acceptance. Note that the mixed-event distribution is limited to
the interval $\left|\Delta\eta\right|<1$: the decision to limit the mixed-event correction, and thus the whole analysis, to this range was taken in
order to avoid the so-called ``wing effect", i.e. the wing-like structures arising in the correlation distribution at large $\Delta\eta$ due to the
limited filling of the correlation bins in that region. The event mixing is calculated in the \textit{AliHFCorrelator} class and is computed in the same way for each D meson.
